---
title: "Analysis of influencing factors for force use in New York City’s Stop, Question, and Frisk"
output: 
  html_document:
    
    toc: true
    fig_caption: yes
    number_sections: yes
highlight: monokai
code_folding: show
author:
  - Yu Liang, Wenzheng Yin, Haiyang Lu
date: "2023-10-18"
editor_options: 
  markdown: 
    wrap: sentence
---

# Exploratory part

```{r message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}
# Load necessary packages
library(nnet)
library(mice)
library(lattice)
library(ggplot2)
library(gridExtra)
library(splines)
library(dplyr)
library(latticeExtra) # for binnedplot
library(arm)
library(pROC)
# load the dataset
load("D:/Users/10567/Desktop/regression/big assignment/sqf_fryer_2003_2013.Rdata")
```

```{r cache=FALSE}
summary(d2)
```

From the summary, we can see that the data types of many variables are inconsistent with their actual meanings, so firstly we change them.

```{r echo=FALSE, cache=TRUE}
# change the data type
d2$force <- as.factor(d2$force)
d2$gender <- as.factor(d2$gender)
d2$age2 <- as.integer(d2$age2)
d2$daytime <- as.factor(d2$daytime)
d2$inout2 <- as.factor(d2$inout2)
d2$offunif2 <- as.factor(d2$offunif2)
d2$typeofid2 <- as.factor(d2$typeofid2)
d2$othpers2 <- as.factor(d2$othpers2)
d2$year <- as.numeric(d2$year)
# delete the ignorable columns(from the describtion in assignment)
d2n<-subset(d2,select = -c(force2,pct))
summary(d2n)
```

From the summary, we can see that: 1, There are 8 variables including NA values: race2, gender, age2, daytime, inout2, offunif2, typeofid2, othpers2.
2, Apart from **force** and **age2**, other variables can be treated as binary categorical variables.

## Density plot for different variables

```{r echo=FALSE, cache=TRUE}
plot1<-list()
d2n_classVariable <- subset(d2n,select = -c(age2,year))
column_names <- colnames(d2n_classVariable)
for (j in 1:20) {
  name <- column_names [j]
  result <- data.frame(table(d2n_classVariable[, j],useNA = "ifany"))
  result$percentage <- (result$Freq / sum(result$Freq))
  
  df <- data.frame(x = result$Var1, y = result$percentage)
  plot1[[j]] <- ggplot(data = df, mapping = aes(x = x, y = y)) +
    geom_bar(stat = 'identity',na.rm = FALSE)+
    xlab(name)+ylab("Percentage")
  
}

#age
x_labels <- c("10", "30", "50", "70", "90", NA)
d2n_age2<-d2n[,4]
result <- data.frame(table(d2n_age2,useNA = "ifany"))
result$percentage <- (result$Freq / sum(result$Freq))
df <- data.frame(x = result$d2n_age2, y = result$percentage)
plot1[[21]] <- ggplot(data = df, mapping = aes(x = x, y = y)) +
  geom_bar(stat = 'identity', na.rm = FALSE) +
  scale_x_discrete(breaks = x_labels, labels = x_labels) +
  xlab("age2") + ylab("Percentage")
   
grid.arrange(grobs = plot1, ncol = 5,norw=4)
```

From the bar and density plots, we get below information for different variables,

1.  For force: In most cases, the police didn't use force in a stop and frisk interaction.
    The total number of remaining samples being used different types of force only accounts for a small portion.
    Therefore, we decide to focus on the problem **if** the police will use force in different situations.
    Specifically, we will consider the force taking values from 1\~7 as the same value 1, representing that force has been used.

2.  For variables related with personal information including race2, gender and age2: From the bar and density plots, we can notice that the civilian investigated are not evenly distributed based on the above information.
    For example, the black, the male or the pedestrians aged around 20 take up a larger proportion than others.
    What' more, these 3 variables exhibit an obvious skewed distribution but it's reasonable since all the samples in the dataset are "stopped" and not generated from random sampling.

3.  For variables starting with 'cs': They describes Civilians' suspicious behaviors.
    And most of these variables take the value of "N".
    Since the accumulated number of "Y" in these variables can reflect the civilian's **suspicion level**, we want to establish a new feature so that all of this information can be aggregated.
    Specifically, we will create a new variable **cs** whose value is the accumulated number of "Y" in these 10 "cs-"starting variables.
    Obviously the larger **cs** is, the more suspicious we consider the civilian to be.
    By creating **cs**, we ignore the specific suspicious behavior while retaining a measure of its level of suspicion, which can reduce noise in our subsequent analysis.

4.  A remarkable variable is **daytime**, the missing data percentage of which is 13% and is much larger than any other variable.
    In addition, another variable "ac_time" also includes the impact of time on force use.
    So we decide to remove this variable in subsequent analysis.

5.  As for ac-incid and ac-time, there is no missing value.
    And there is no much difference between the proportion of "N" and "Y" for both.

6.  inouts, offunit2 and otherpers2, all of two variables with little missing data are observed a slight skew.

7.  typeofid2 has four levels, the first three of which can be regarded as the same level: agree to provide ID.
    Specifically, we will transfer typeofid2 into a binary variable, denoting "R" as "0" and the other three as "1".

8.  As for years, we think it cannot be used for prediction.
    Because intuitively, the passage of years does not directly affect the force use.
    Even if there is an impact, it is also indirect (such as through the implementation of some certain policies).
    Therefore, we won't be able to explain the meaning of its coefficient in the model, nor can we guarantee the explanatory power of the model for future data.
    As a result we decide to delete this variable before we build the model.

## Handle the missing value: Multiple imputation

### The background of Multiple Interpolation

Multiple imputation typically involves three main steps: 1.
Imputation: Impute missing values in each dataset.
Imputation can be done using various methods, such as regression imputation, predictive mean matching, or other imputation models.
Each imputed dataset represents one possible set of missing data replacements.
2.
Analysis: Analyze each imputed dataset separately using the statistical analysis you intend to perform (e.g., regression analysis, hypothesis testing, or data visualization).
3.
Pooling: Combine the results from each imputed dataset to obtain a single set of parameter estimates and standard errors.
This is typically done using Rubin's rules, which take into account both within-imputation variability and between-imputation variability.

But since this dataset is too large and pooling will be very computationally expensive so we only analysis on one imputed dataset.

In order to achieve better results in multiple imputation, we hope to utilize the relationships between various variables as much as possible.
Therefore we aim to exclude situations where missing values center at one specific case.
We draw the cross tabulation of 2 variables to achieve this objective.
Take race2 and gender for example.

```{r echo=FALSE}
table(d2n$race2, is.na(d2n$gender)) # why we can impute the data
```

There is no abnormality displayed in the table.

What's more we can draw the missing data pattern.

```{r echo=FALSE, cache = TRUE}
missing_data_pattern<- md.pattern(d2,rotate.names=TRUE)
```

From this plot we can see that although sometimes multiple variables are missing together, there are no dominant patterns.

```{r echo=FALSE, cache = TRUE}
set.seed(123)

# Perform imputation
# mice_data <- mice(d2n, m = 1)

# In order to shorten the time required for .rmd to generate documents, we stored the "mice_data" after multiple imputations
load("D:/Users/10567/Desktop/regression/big assignment/mice_original.Rdata")
# Export imputed data
imputed_data <- complete(mice_data,1) #mice_data is mice(d2n, m = 1)
```

### Multiple imputation diagnostics

We do the imputation with mice() and we can do diagnostics directly.
We observe the distribution of **age2** before and after the imputation and it doesn't change much, which implies the quality of the imputed dataset is acceptable.
We didn't show all the results but they are all similar.

```{r cache = TRUE}
densityplot(mice_data)
```

## Feature engineering

From the discussion above, we build new features based on the imputed data.

```{r echo=FALSE, cache = TRUE}
# build "cs"
for (i in (ncol(imputed_data) - 10):(ncol(imputed_data)-1)) {
  imputed_data[,i] <- ifelse(imputed_data[,i] == "Y", 1, ifelse(imputed_data[,i] == "N", 0, imputed_data[,i]))
}
imputed_data$cs <- rowSums(imputed_data[, (ncol(imputed_data) - 10):(ncol(imputed_data)-1)])

# change force&typeofid2 into a 0-1 variable
imputed_data$force <- ifelse(imputed_data$force != 0, 1, 0)
imputed_data$force <- as.factor(imputed_data$force)
imputed_data$typeofid2 <- ifelse(imputed_data$typeofid2 == "R",0,1)
imputed_data$typeofid2 <- as.factor(imputed_data$typeofid2)

#delete the "cs-" starting variables
imputed_data <- subset(imputed_data,select = -c(cs_objcs, cs_descr, cs_casng, cs_lkout, cs_cloth, cs_drgtr, cs_furtv, cs_vcrim, cs_bulge, cs_other,year,daytime))

summary(imputed_data)
```

## Force use v.s. single variable

```{r echo=FALSE, cache = TRUE}
#plot percentage of different force on each category in each variable
plot2<-list()
for (i in c(2:11)) {
    frequency_table <- table(imputed_data[,i], imputed_data[,1])
    prop_table <- prop.table(frequency_table, margin = 1)
    df<-as.data.frame(prop_table)
    
    plot2[[i-1]]<-ggplot(df, aes(x = Var1, y = Freq, fill = Var2)) +
      geom_bar(stat = "identity", position = "dodge", color = "black") +
      labs(x = colnames(imputed_data)[i], y = "Percentage",fill="force") +
      scale_fill_manual(values = c("skyblue","yellow")) +
      theme_minimal()
      
}

grid.arrange(grobs = c(plot2[1:2],plot2[4:10]), ncol = 3,norw=3)
print(plot2[[3]]+scale_x_discrete(breaks = seq(10, 80, by = 5)))
```

From these plot we can form a basic impression on how each variable affect the force.

For example, there is a significant difference in force use in different **race2**, **gender**,...,groups, which implies that these variables maybe strong predictors in our following analysis and shows their specific impact on force use.
For example, force is used more on gender0 group(male) than gender1 group(female).
For other variables the analysis is similar.

## Spearman correlation matrix

We draw the correlation plot to explore the potential collinearity between variables.

```{r echo=FALSE, cache = TRUE}
#Spearman correlation matrix
cp<-cor(data.matrix(imputed_data),method="spearman")
ord<-rev(hclust(as.dist(1-abs(cp)))$order)
colPal<-colorRampPalette(c("blue","yellow"),space="rgb")(100)

p<-levelplot(cp[ord,ord],
          xlab="",
          ylab="",
          col.regions=colPal,
          at=seq(-1,1,length.out=100),
          colorkey=list(space="top",labels=list(cex=1.5)),
          scales=list(x=list(rot=45),
                      y=list(draw=FALSE),
                      cex=1.2)
          )
print(p)
```

From the plot we can observe a positive correlation between ac_time and ac_incid but not very strong.
There is not enough evidence for us to delete any variable in this step.

## Add1(),drop1() and F-test

```{r cache = TRUE}
form1 <- force~race2 + gender + age2 + inout2 + ac_incid + ac_time + offunif2 + typeofid2 + othpers2 + cs

model_full <- glm(form1,family = binomial(link = "logit"), 
                  contrasts = list(race2="contr.sum", gender="contr.sum", inout2="contr.sum", ac_incid="contr.sum", ac_time="contr.sum", offunif2="contr.sum", typeofid2="contr.sum", othpers2="contr.sum"),
                  data=imputed_data)

model_null <- glm(force~1, family = binomial(link = "logit"), data = imputed_data)

AddTermModel<-add1(model_null,model_full, test="LRT")
DropTermModel<-drop1(model_full, test="LRT")

print(AddTermModel)
print(DropTermModel)
```

From the result of F-test, we can say that all the variables included are significant and we should keep them.

# Analysis part

We choose the logit regression model for our study since it's a binary classification problem.

## Model construction

First of all, we will build a *logit_m1* with all variables included.

Intuitively, there may exist a nonlinear effect in **age**.
Because for too young and too old civilians the police should be less inclined to use force than adult civilians.

What's more, we consider an interaction effect between **ac_incid** and **ac_time**.
We guess if the stop occurs both in an area of high crime incidence and at a time of day that fit crime incidence, the police may be more alert than usual and be more likely to use force.

We build three more models which consider a nonlinear effect(*logit_md2*), an interaction effect(*logit_m3*), a nonlinear and interaction effect(*logit_md4*).

```{r cache = TRUE}
# 0-1 response with no interaction & splines
form1 <- force~race2+gender+age2+inout2+ac_incid+ac_time+offunif2+typeofid2+othpers2+cs
# 0-1 response with ac_incid*ac_time
form2 <- force~race2+gender+age2+inout2+ac_incid*ac_time+offunif2+typeofid2+othpers2+cs
# 0-1 response with splines
form3 <- force~race2+gender+ns(age2,df=3)+inout2+ac_incid+ac_time+offunif2+typeofid2+othpers2+cs
# 0-1 response with ac_incid*ac_time & splines
form4 <- force~race2+gender+ns(age2,df=3)+inout2+ac_incid*ac_time+offunif2+typeofid2+othpers2+cs

# build the logit models  
logit_md1 <- glm(form1, family = binomial(link=logit), data = imputed_data)
logit_md2 <- glm(form2, family = binomial(link=logit), data = imputed_data)
logit_md3 <- glm(form3, family = binomial(link=logit), data = imputed_data)
logit_md4 <- glm(form4, family = binomial(link=logit), data = imputed_data)
```

### Anova

```{r cache = TRUE}
anova(logit_md1, logit_md2, test = "LRT")
anova(logit_md1, logit_md3, test = "LRT")
anova(logit_md3, logit_md4, test = "LRT")
```

From the result of anova, we can say that both interaction and nonlinear effects are worth consideration.

### Explanation of the models

```{r echo=FALSE}
md_list <- list(logit_md1, logit_md2, logit_md3, logit_md4)
for (md in md_list) {
  print(summary(md))
}
```

1.  All the variables are significant so their values are meaningful.
2.  The value of variables represents the way how they influence the probability of being used force when stopped. Take *logit_md1* for example, the coefficient of **gender1** means that when all other variables remain the same, **gender1**(female) is less likely to be used force by a probability of 0.54.

## Model diagnostic

### raw deviance residuals

Take the *logit_md1* for example.
We plot its deviance/person residuals.

```{r echo=FALSE, warning=FALSE, cache = TRUE}
forceDiag<-transform(
  imputed_data,
  .fitted=predict(logit_md1,type = "response"),
  .deviance=residuals(logit_md1, type = "deviance"),
  .pearson=residuals(logit_md1, type = "pearson")
)

p1<-qplot(.fitted, .deviance,data=forceDiag,geom="hex")+
  geom_smooth(linewidth=1)+
  xlab("fitted values")+ylab("deviance residuals")
p2<-qplot(.fitted,.pearson,data=forceDiag,geom="hex")+
  geom_smooth(linewidth=1)+
  xlab("fitted values")+ylab("pearson residuals")

grid.arrange(p1,p2,ncol=2)

```

In this plot, we get two curves for both kinds of residuals.
It's because the "force2" is a binary variable and consequently for any fitted response there are only 2 values for the deviance.
As a result, this raw residual plot do not exhibit the same pattern and could not be used to test homoscedasticity which we might expect in linear regression model's residual plot.

### binned residual

A binned residual plot is a graphical method for assessing the goodness of fit and the distribution of residuals in a regression model, especially when dealing with a large number of data points.
It is commonly used in linear regression and generalized linear models, including logistic regression.

The binned residual-fitted plot involves the following steps:

1.  Divide the range of fitted values into a series of bins or intervals.
2.  Calculate the mean(or median) of the residuals for each bin. These are the observed residuals within each bin.
3.  Plot the observed residuals against the corresponding bin's center or average fitted value. This results in a scatter plot with bins.
4.  Optionally, overlay reference lines, such as a horizontal line at 0, to assess the overall distribution of residuals.

#### residual-fitted plot

We use fitting on subsets with 1,500,000 observations to obtain binned residual plots, as the entire dataset exceeded the computational power of binnedplot() and it will cause errors.

This can also reflect our concerns because the subset is generated through random sampling and big enough.

```{r echo=FALSE, cache = TRUE}
set.seed(123)
subset_size <- 1500000
subset_indices <- sample(nrow(imputed_data), subset_size)

subset_md1 <- update(logit_md1, subset = subset_indices)
subset_md2 <- update(logit_md2, subset = subset_indices)
subset_md3 <- update(logit_md3, subset = subset_indices)
subset_md4 <- update(logit_md4, subset = subset_indices)

```

```{r echo=FALSE, cache = TRUE}
# Create a binned residual plot
binnedplot(predict(subset_md1,type = "response"), 
         residuals(subset_md1,type = "response"), 
         # type = "response" means we take the 0-1 loss
         nclass = NULL, # let binnedplot() calculate appropriate number of bins itself
         xlab = "Expected Values", 
         ylab = "Average residual", 
         ylim = c(-0.15, 0.15),
         main = "Binned residual plot (Subset) - logit_md1", 
         cex.pts = 0.4, 
         col.pts = 1, 
         col.int = "gray")
```

```{r echo=FALSE, cache = TRUE}
# Create a binned residual plot
binnedplot(predict(subset_md2,type = "response"), 
         residuals(subset_md2,type = "response"), 
         # type = "response" means we take the 0-1 loss
         nclass = NULL, # let binnedplot() calculate appropriate number of bins itself
         xlab = "Expected Values", 
         ylab = "Average residual", 
         ylim = c(-0.15, 0.15),
         main = "Binned residual plot (Subset) - logit_md2", 
         cex.pts = 0.4, 
         col.pts = 1, 
         col.int = "gray")
```

```{r echo=FALSE, cache = TRUE}
# Create a binned residual plot
binnedplot(predict(subset_md3,type = "response"), 
         residuals(subset_md3,type = "response"), 
         # type = "response" means we take the 0-1 loss
         nclass = NULL, # let binnedplot() calculate appropriate number of bins itself
         xlab = "Expected Values", 
         ylab = "Average residual", 
         ylim = c(-0.15, 0.15),
         main = "Binned residual plot (Subset) - logit_md3", 
         cex.pts = 0.4, 
         col.pts = 1, 
         col.int = "gray")
```

```{r echo=FALSE, cache = TRUE}
# Create a binned residual plot
binnedplot(predict(subset_md4,type = "response"), 
         residuals(subset_md4,type = "response"), 
         # type = "response" means we take the 0-1 loss
         nclass = NULL, # let binnedplot() calculate appropriate number of bins itself
         xlab = "Expected Values", 
         ylab = "Average residual", 
         ylim = c(-0.15, 0.15),
         main = "Binned residual plot (Subset) - logit_md4", 
         cex.pts = 0.4, 
         col.pts = 1, 
         col.int = "gray")
```

The binned residuals plots show that all 4 models are good fits since the means are around 0 and there are no significant patterns for the plot.

#### residual-univariate plot

For continous variable we make the residual-univariate plot.
The residual should be around 0 and there should be no significant pattern.

```{r echo=FALSE, cache = TRUE}
binnedplot(x=imputed_data[subset_indices,]$age2, 
           residuals(subset_md1, type = "response"), 
           nclass = NULL, 
           xlab = "age2", 
           ylab = "Average residual", 
           ylim = c(-0.04, 0.04),
           main = "Binned residual plot (Subset) - logit_md1", 
           cex.pts = 0.4, 
           col.pts = 1, 
           col.int = "gray")
```

```{r echo=FALSE, cache = TRUE}
binnedplot(x=imputed_data[subset_indices,]$age2, 
           residuals(subset_md3, type = "response"), 
           nclass = NULL, 
           xlab = "age2", 
           ylab = "Average residual", 
           ylim = c(-0.04, 0.04),
           main = "Binned residual plot (Subset) - logit_md3", 
           cex.pts = 0.4, 
           col.pts = 1, 
           col.int = "gray")
```

```{r echo=FALSE, cache = TRUE}
binnedplot(x=imputed_data[subset_indices,]$age2, 
           residuals(subset_md4, type = "response"), 
           nclass = NULL, 
           xlab = "age2", 
           ylab = "Average residual", 
           ylim = c(-0.04, 0.04),
           main = "Binned residual plot (Subset) - logit_md4", 
           cex.pts = 0.4, 
           col.pts = 1, 
           col.int = "gray")
```

The inclusion of splines is not changing the residual-age2 plot.
All 3 are acceptable.

For categorical variable we calculate mean residuals for each group.
It should be around 0 and the difference between different group shouldn't be too large.
We only take some for example.

```{r echo=FALSE, cache=TRUE}
forceDiag%>%
  group_by(gender)%>%
  summarise(mean_resid=mean(.deviance))

forceDiag%>%
  group_by(cs)%>%
  summarise(mean_resid=mean(.deviance))
```

From the results we can see that only when **cs** values 9 and 10 the residual is abnormal.
And it's because the samples with **cs**\>=9 are very little.

## Model assessment

### ROC curve

A ROC curve is constructed by plotting the true positive rate (TPR) against the false positive rate (FPR).
It provides a visual representation of a model's ability to distinguish between two classes.
The AUC measures the overall performance of the classification model.
A perfect model has an AUC of 1, while a random model has an AUC of 0.5.
The higher the AUC, the better the model's discriminatory power.

```{r echo=FALSE, cache=TRUE}
predicted_prob <- predict(logit_md1, type = "response")
roc_curve <- roc(response = imputed_data$force, predictor = predicted_prob)
## Plot ROC curve
plot(roc_curve, col = "blue", main = "ROC Curve", lwd = 2)
abline(a = 0, b = 1, col = "red", lwd = 2, lty = 2)
text(0.8, 0.2, paste("AUC =", round(auc(roc_curve), 2)), col = "blue", cex = 1.2)
```

We only show ROC curve for one model but actually we've calculate the AUC for all 4 models.The AUC for 4 models are all 0.63, which means there is no clear advantage of one model over the others in terms of Sensitivity and Specificity.

### CrossValidation

We alse use CrossValidation to evalue 4 models' performances.

```{r echo=FALSE, cache = TRUE}
testCV <- function(form, data, B = 1, k = 5) {
  n <- nrow(data)
  PEcv <- vector("list", B)
  squared_devaince <- numeric(n)
  for(b in 1:B) {
    ## Generating the random division into groups
    group <- sample(rep(1:k, length.out = n))
    for(i in 1:k) {
      train_data=data[group != i, ]
      test_data=data[group == i, ]
      modelcv <- glm(form,family = binomial(link = "logit"), data = train_data)
      muhat <- predict(modelcv, newdata = test_data, type="response")
      squared_devaince[group == i]<-  -2*( test_data$force * log(muhat) + (1-test_data$force) * log(1-muhat) )
    }
    PEcv[[b]] <- squared_devaince
  }
  mean(unlist(PEcv))
}
imputed_data$force<-as.integer(as.character(imputed_data$force))

deviance1<-testCV(logit_md1, imputed_data) #1.009966727
deviance2<-testCV(logit_md2, imputed_data) #1.009712631
deviance3<-testCV(logit_md3, imputed_data) #1.009773304
deviance4<-testCV(logit_md4, imputed_data) #1.009523049


deviance_df <- data.frame(VariableName = c("deviance1", "deviance2", "deviance3", "deviance4"), Value = c(deviance1, deviance2, deviance3, deviance4))

print(deviance_df)

```

From the results of cross validation, we can see that the prediction accuracy for these models are basically the same, while *logit_md1* has the simplest form.

## Discussion and conclusion

In conclusion, **logit_md1** should be the final model we choose.

## Plus: interval estimation

We do the interval estimation for the coefficient of *logit_md1*.
We only take **age2** for example.

```{r cache = TRUE}
# The standard interval
confint.default(logit_md1,"age2")
# The likelihood interval
confint(logit_md1,"age2")
```

```{r cache = TRUE}
# nonparametric bootstrap
B<- 5
n<- nrow(imputed_data)
beta<- numeric(B)
for(b in 1:B){
  i<- sample(n,n,replace=TRUE)
  bootGlm<-glm(form1,family = binomial(link = "logit"), data = imputed_data[i,])
  beta[b]<-coefficients(bootGlm)["age2"]
}
```

```{r cache = TRUE}
# parametric bootstrap
parbeta<-numeric(B)
d2Samp<-imputed_data
for(b in 1:B){
  d2Samp$force<-simulate(logit_md1)[,1]
  bootGlm<-glm(form1,family = binomial(link = "logit"), data = d2Samp)
  parbeta[b]<-coefficients(bootGlm)["age2"]
}
```

```{r cache = TRUE}
sebeta<-sd(beta)
separbeta<-sd(parbeta)
```

```{r cache = TRUE}
# standard error based on ordinary analytic approximations
betahat<-coefficients(logit_md1)["age2"]

# interval based on nonparametric bootstrap
betahat+1.96*sebeta*c(-1,1)
# interval based on parametric bootstrap
betahat+1.96*separbeta*c(-1,1)
```

We derive 4 interval estimations for the coefficient for **age** and they are basically the same, which can also provide evidence that the model is good.
Because if it's not, there would be a difference between the intervals derived from parametric and nonparametric bootstrapping.
